Methodology for Assessing the State of the Practice for Domain X

### 2020-03-31 StateOfPractice/Methodology/Methodology.tex
update tool tests

\subsection{Tool Test - HubListener}
\ad{This section is currently a note of unorganized contents. Most parts will be
removed or relocated.}

\href{https://github.com/pjmc-oliveira/HubListener}{GitHub repo}

@@

>>>>

\subsection{Tool Tests}
\ad{This section is currently a note of unorganized contents. Most parts will beremoved or relocated.}

Most tests were done targeting to the repo of 3D Slicer
\href{https://github.com/tomgi/git_stats}{GitHub repo}

\subsubsection{git-stats}
\href{https://github.com/tomgi/git_stats}{GitHub repo}

Test results:
\href{http://git-stats-slicer.ao9.io/}{http://git-stats-slicer.ao9.io/} the
results are output as webpages, so I hosted for you to check. Data can be
downloaded as spreadsheets.

\subsubsection{git-of-theseus}
\href{https://github.com/erikbern/git-of-theseus}{GitHub repo}

Test results: It took about 100 minutes for one repo on a 8 core 16G ram Linux
machine. It only outputs graphs.

\subsubsection{hercules}
\href{https://github.com/src-d/hercules}{GitHub repo}

Test results: this one seems to be promising, but the installation is
complicated with various errors.

\subsubsection{git-repo-analysis}
\href{https://github.com/larsxschneider/git-repo-analysis}{GitHub repo}

\subsubsection{HubListener}
\href{https://github.com/pjmc-oliveira/HubListener}{GitHub repo}

@@

\subsubsection{gitinspector}
\href{https://github.com/ejwa/gitinspector}{GitHub repo}

Test results: it doesn't work well. Instead of creating output results, it
prints the results directly in the console.
